lfl: An \R{} Package for Linguistic Fuzzy Logic

### 2021-06-09 chunks/chunk-casestudy-assoc-lcut.tex
updated assoc case study

\begin{Schunk}
% --begin: "casestudy-assoc-lcut"
\begin{Sinput}
ldata <- lcut(data)
colnames(ldata)
\end{Sinput}
\begin{Soutput}
##  [1] "position=accountant" "position=manager"    "position=worker"    
##  [4] "ex.sm.age"           "si.sm.age"           "ve.sm.age"          
##  [7] "sm.age"              "ml.sm.age"           "ro.sm.age"          
## [10] "qr.sm.age"           "vr.sm.age"           "ty.me.age"          
## [13] "me.age"              "ml.me.age"           "ro.me.age"          
## [16] "qr.me.age"           "vr.me.age"           "ex.bi.age"          
## [19] "si.bi.age"           "ve.bi.age"           "bi.age"             
## [22] "ml.bi.age"           "ro.bi.age"           "qr.bi.age"          
## [25] "vr.bi.age"           "employed"            "not.employed"       
## [28] "ex.sm.salary"        "si.sm.salary"        "ve.sm.salary"       
## [31] "sm.salary"           "ml.sm.salary"        "ro.sm.salary"       
## [34] "qr.sm.salary"        "vr.sm.salary"        "ty.me.salary"       
## [37] "me.salary"           "ml.me.salary"        "ro.me.salary"       
## [40] "qr.me.salary"        "vr.me.salary"        "ex.bi.salary"       
## [43] "si.bi.salary"        "ve.bi.salary"        "bi.salary"          
## [46] "ml.bi.salary"        "ro.bi.salary"        "qr.bi.salary"       
## [49] "vr.bi.salary"
\end{Soutput}
%
% --end: "casestudy-assoc-lcut"
\end{Schunk}

>>>>

\begin{Schunk}
% --begin: "casestudy-assoc-lcut"
\begin{Sinput}
ldata <- lcut(iris)
colnames(ldata)
\end{Sinput}
\begin{Soutput}
##  [1] "ex.sm.Sepal.Length" "si.sm.Sepal.Length" "ve.sm.Sepal.Length"
##  [4] "sm.Sepal.Length"    "ml.sm.Sepal.Length" "ro.sm.Sepal.Length"
##  [7] "qr.sm.Sepal.Length" "vr.sm.Sepal.Length" "ty.me.Sepal.Length"
## [10] "me.Sepal.Length"    "ml.me.Sepal.Length" "ro.me.Sepal.Length"
## [13] "qr.me.Sepal.Length" "vr.me.Sepal.Length" "ex.bi.Sepal.Length"
## [16] "si.bi.Sepal.Length" "ve.bi.Sepal.Length" "bi.Sepal.Length"   
## [19] "ml.bi.Sepal.Length" "ro.bi.Sepal.Length" "qr.bi.Sepal.Length"
## [22] "vr.bi.Sepal.Length" "ex.sm.Sepal.Width"  "si.sm.Sepal.Width" 
## [25] "ve.sm.Sepal.Width"  "sm.Sepal.Width"     "ml.sm.Sepal.Width" 
## [28] "ro.sm.Sepal.Width"  "qr.sm.Sepal.Width"  "vr.sm.Sepal.Width" 
## [31] "ty.me.Sepal.Width"  "me.Sepal.Width"     "ml.me.Sepal.Width" 
## [34] "ro.me.Sepal.Width"  "qr.me.Sepal.Width"  "vr.me.Sepal.Width" 
## [37] "ex.bi.Sepal.Width"  "si.bi.Sepal.Width"  "ve.bi.Sepal.Width" 
## [40] "bi.Sepal.Width"     "ml.bi.Sepal.Width"  "ro.bi.Sepal.Width" 
## [43] "qr.bi.Sepal.Width"  "vr.bi.Sepal.Width"  "ex.sm.Petal.Length"
## [46] "si.sm.Petal.Length" "ve.sm.Petal.Length" "sm.Petal.Length"   
## [49] "ml.sm.Petal.Length" "ro.sm.Petal.Length" "qr.sm.Petal.Length"
## [52] "vr.sm.Petal.Length" "ty.me.Petal.Length" "me.Petal.Length"   
## [55] "ml.me.Petal.Length" "ro.me.Petal.Length" "qr.me.Petal.Length"
## [58] "vr.me.Petal.Length" "ex.bi.Petal.Length" "si.bi.Petal.Length"
## [61] "ve.bi.Petal.Length" "bi.Petal.Length"    "ml.bi.Petal.Length"
## [64] "ro.bi.Petal.Length" "qr.bi.Petal.Length" "vr.bi.Petal.Length"
## [67] "ex.sm.Petal.Width"  "si.sm.Petal.Width"  "ve.sm.Petal.Width" 
## [70] "sm.Petal.Width"     "ml.sm.Petal.Width"  "ro.sm.Petal.Width" 
## [73] "qr.sm.Petal.Width"  "vr.sm.Petal.Width"  "ty.me.Petal.Width" 
## [76] "me.Petal.Width"     "ml.me.Petal.Width"  "ro.me.Petal.Width" 
## [79] "qr.me.Petal.Width"  "vr.me.Petal.Width"  "ex.bi.Petal.Width" 
## [82] "si.bi.Petal.Width"  "ve.bi.Petal.Width"  "bi.Petal.Width"    
## [85] "ml.bi.Petal.Width"  "ro.bi.Petal.Width"  "qr.bi.Petal.Width" 
## [88] "vr.bi.Petal.Width"  "Species=setosa"     "Species=versicolor"
## [91] "Species=virginica"
\end{Soutput}
%
% --end: "casestudy-assoc-lcut"
\end{Schunk}

### 2021-06-09 chunks/chunk-casestudy-assoc-reduce.tex
updated assoc case study

\begin{Schunk}
% --begin: "casestudy-assoc-reduce"
\begin{Sinput}
reduce(ldata, rules=lrules, ratio=1)
\end{Sinput}
\begin{Soutput}
## Empty rule base
\end{Soutput}
%
% --end: "casestudy-assoc-reduce"
\end{Schunk}

>>>>

\begin{Schunk}
% --begin: "casestudy-assoc-reduce"
\begin{Sinput}
reduce(ldata, rules=lrules, ratio=1)
\end{Sinput}
\begin{Soutput}
##                                                                                      support
## qr.sm.Petal.Width => Species=setosa                                               0.33333334
## ro.me.Sepal.Width & qr.sm.Petal.Length => Species=setosa                          0.26911455
## ve.sm.Sepal.Length => Species=setosa                                              0.06378584
## ro.me.Sepal.Length & ml.me.Petal.Length & ty.me.Petal.Width => Species=versicolor 0.09947090
## ty.me.Petal.Length => Species=versicolor                                          0.07089734
## ro.bi.Petal.Length => Species=virginica                                           0.17762597
## ml.bi.Petal.Width => Species=virginica                                            0.17133440
## vr.sm.Sepal.Width & ro.bi.Petal.Width => Species=virginica                        0.06244373
## qr.bi.Petal.Length & ro.bi.Petal.Width => Species=virginica                       0.16844945
## vr.bi.Sepal.Length & ro.bi.Petal.Width => Species=virginica                       0.12503819
##                                                                                   lhsSupport
## qr.sm.Petal.Width => Species=setosa                                               0.33333334
## ro.me.Sepal.Width & qr.sm.Petal.Length => Species=setosa                          0.26918504
## ve.sm.Sepal.Length => Species=setosa                                              0.06380372
## ro.me.Sepal.Length & ml.me.Petal.Length & ty.me.Petal.Width => Species=versicolor 0.09948596
## ty.me.Petal.Length => Species=versicolor                                          0.07089734
## ro.bi.Petal.Length => Species=virginica                                           0.17762597
## ml.bi.Petal.Width => Species=virginica                                            0.17133440
## vr.sm.Sepal.Width & ro.bi.Petal.Width => Species=virginica                        0.06244373
## qr.bi.Petal.Length & ro.bi.Petal.Width => Species=virginica                       0.16844945
## vr.bi.Sepal.Length & ro.bi.Petal.Width => Species=virginica                       0.12503819
##                                                                                   rhsSupport
## qr.sm.Petal.Width => Species=setosa                                                0.3333333
## ro.me.Sepal.Width & qr.sm.Petal.Length => Species=setosa                           0.3333333
## ve.sm.Sepal.Length => Species=setosa                                               0.3333333
## ro.me.Sepal.Length & ml.me.Petal.Length & ty.me.Petal.Width => Species=versicolor  0.3333333
## ty.me.Petal.Length => Species=versicolor                                           0.3333333
## ro.bi.Petal.Length => Species=virginica                                            0.3333333
## ml.bi.Petal.Width => Species=virginica                                             0.3333333
## vr.sm.Sepal.Width & ro.bi.Petal.Width => Species=virginica                         0.3333333
## qr.bi.Petal.Length & ro.bi.Petal.Width => Species=virginica                        0.3333333
## vr.bi.Sepal.Length & ro.bi.Petal.Width => Species=virginica                        0.3333333
##                                                                                   confidence
## qr.sm.Petal.Width => Species=setosa                                                1.0000000
## ro.me.Sepal.Width & qr.sm.Petal.Length => Species=setosa                           0.9997382
## ve.sm.Sepal.Length => Species=setosa                                               0.9997197
## ro.me.Sepal.Length & ml.me.Petal.Length & ty.me.Petal.Width => Species=versicolor  0.9998486
## ty.me.Petal.Length => Species=versicolor                                           1.0000000
## ro.bi.Petal.Length => Species=virginica                                            1.0000000
## ml.bi.Petal.Width => Species=virginica                                             1.0000000
## vr.sm.Sepal.Width & ro.bi.Petal.Width => Species=virginica                         1.0000000
## qr.bi.Petal.Length & ro.bi.Petal.Width => Species=virginica                        1.0000000
## vr.bi.Sepal.Length & ro.bi.Petal.Width => Species=virginica                        1.0000000
\end{Soutput}
%
% --end: "casestudy-assoc-reduce"
\end{Schunk}

### 2021-06-09 chunks/chunk-casestudy-assoc-searchrules.tex
updated assoc case study

\begin{Schunk}
% --begin: "casestudy-assoc-searchrules"
\begin{Sinput}
lrules <- searchrules(ldata,
                      lhs=grep('^Species=', colnames(ldata), invert=TRUE),
                      rhs=grep('^Species=', colnames(ldata)),
                      minSupport=0.05)
\end{Sinput}
\begin{Soutput}
## Warning in min(rhs): no non-missing arguments to min; returning Inf
\end{Soutput}
\begin{Soutput}
## Warning in max(rhs): no non-missing arguments to max; returning -Inf
\end{Soutput}
\begin{Sinput}
ldf <- as.data.frame(lrules)
head(ldf[order(ldf$support, decreasing=TRUE), ])
\end{Sinput}
\begin{Soutput}
## Error in order(ldf$support, decreasing = TRUE): argument 1 is not a vector
\end{Soutput}
%
% --end: "casestudy-assoc-searchrules"
\end{Schunk}

>>>>

\begin{Schunk}
% --begin: "casestudy-assoc-searchrules"
\begin{Sinput}
lrules <- searchrules(ldata,
                      lhs=grep('^Species=', colnames(ldata), invert=TRUE),
                      rhs=grep('^Species=', colnames(ldata)),
                      minSupport=0.05)
ldf <- as.data.frame(lrules)
head(ldf[order(ldf$support, decreasing=TRUE), ])
\end{Sinput}
\begin{Soutput}
##                                        support lhsSupport rhsSupport
## qr.sm.Petal.Width => Species=setosa  0.3333333  0.3333333  0.3333333
## ro.sm.Petal.Length => Species=setosa 0.3333333  0.3333333  0.3333333
## ml.sm.Petal.Length => Species=setosa 0.3329695  0.3329695  0.3333333
## ro.sm.Petal.Width => Species=setosa  0.3329422  0.3329422  0.3333333
## ml.sm.Petal.Width => Species=setosa  0.3291277  0.3291277  0.3333333
## sm.Petal.Length => Species=setosa    0.3230208  0.3230208  0.3333333
##                                      confidence
## qr.sm.Petal.Width => Species=setosa           1
## ro.sm.Petal.Length => Species=setosa          1
## ml.sm.Petal.Length => Species=setosa          1
## ro.sm.Petal.Width => Species=setosa           1
## ml.sm.Petal.Width => Species=setosa           1
## sm.Petal.Length => Species=setosa             1
\end{Soutput}
%
% --end: "casestudy-assoc-searchrules"
\end{Schunk}
